---
title: "R Notebook"
output: html_notebook
---


```{r}
library(DMwR)
```

```{r}
source("csv_to_db.R")
```

```{r}
con = connect_db()
```

Total number of rows or observations in eddetails table
```{r}
dbGetQuery(con, "SELECT COUNT(*) FROM eddetails;")
```

head of eddetails
```{r}
dbGetQuery(con, "SELECT * FROM eddetails LIMIT 5;")
```

Number of distinct categories by indicator_code in eddetails
```{r}
dbGetQuery(con, "SELECT COUNT(DISTINCT indicator_code) FROM eddetails;")
```

Number of distinct countries, continents or regions
```{r}
dbGetQuery(con, "SELECT COUNT(DISTINCT country_name) FROM eddetails;")
```

List of distinct countries, continents or regions
```{r}
dbGetQuery(con, "SELECT DISTINCT country_name FROM eddetails;")
```



Surveys with count who where successfully conducted in at least 200 regions
```{r}
dbGetQuery(con, "SELECT indicator_code, COUNT(*) FROM eddetails GROUP BY indicator_code HAVING COUNT(*) >= 200 ORDER BY COUNT(*) DESC;")
```


get list of definition of surveys from statseries table, who were successfully conducted in at least 200 regions.
```{r}
# get list of indicator_code for surveys

code_df = dbGetQuery(con, "SELECT indicator_code FROM eddetails GROUP BY indicator_code HAVING COUNT(*) >= 200 ORDER BY COUNT(*) DESC;") # dataframe of codes
code_list = code_df[,1]

```
```{r}
# head of statseries table
dbGetQuery(con, "SELECT * FROM statseries LIMIT 5;")
```


```{r}
dbGetQuery(con, "SELECT COUNT(DISTINCT long_definition) FROM statseries;")
```



Thats the answer for now!
```{r}
most_frequent_eddetails = "SELECT indicator_code FROM eddetails GROUP BY indicator_code HAVING COUNT(*) >= 200"
dbGetQuery(con, paste("SELECT * FROM statseries WHERE indicator_code IN (", most_frequent_eddetails, ");", sep = ""))
```

Selected surveys are:

SL.UEM.TOTL.FE.ZS : Unemployment, F
SL.UEM.TOTL.MA.ZS : Unemployment, M
SL.TLF.TOTL.FE.ZS : Female Labor Force %
UIS.OE.56.40510 : Foreign Education


In order to plot all these graphs by a single selection menu, we need to skip countries that don't have data for all 4 categories.
```{r}
# find count for 4 surveys in eddetails.
select_surveys_list = c("SL.UEM.TOTL.FE.ZS", "SL.UEM.TOTL.MA.ZS", "SL.TLF.TOTL.FE.ZS", "UIS.OE.56.40510")

survey_list_string = paste(select_surveys_list, collapse = "', '")

dbGetQuery(con, paste("SELECT indicator_code, COUNT(*) FROM eddetails WHERE indicator_code IN ('", survey_list_string, "') GROUP BY indicator_code;", sep = ""))
```

Most probably there are 206 countries common along all 4 surveys. Create csv file for each survey dataframe.


```{r}
# check if country codes are unique for each country or not
dbGetQuery(con, "SELECT COUNT(DISTINCT country_name), COUNT(DISTINCT country_code) from eddetails;")
```
Great!! They are unique. Now get vector for country codes present in each of 4 surveys.
```{r}

country_list1 = dbGetQuery(con, paste("SELECT DISTINCT country_code FROM eddetails WHERE indicator_code = '", select_surveys_list[1], "';", sep = ""))

country_list2 = dbGetQuery(con, paste("SELECT DISTINCT country_code FROM eddetails WHERE indicator_code = '", select_surveys_list[2], "';", sep = ""))

country_list3 = dbGetQuery(con, paste("SELECT DISTINCT country_code FROM eddetails WHERE indicator_code = '", select_surveys_list[3], "';", sep = ""))

country_list4 = dbGetQuery(con, paste("SELECT DISTINCT country_code FROM eddetails WHERE indicator_code = '", select_surveys_list[4], "';", sep = ""))

```

List of countries that are repeated more than once.
```{r}
dbGetQuery(con, paste("SELECT country_code, COUNT(*) FROM eddetails WHERE indicator_code = '", select_surveys_list[4], "' GROUP BY country_code HAVING COUNT(*) > 1;", sep = ""))
```

```{r}
dbGetQuery(con, paste("SELECT country_code, COUNT(*) FROM eddetails WHERE indicator_code = '", select_surveys_list[2], "' GROUP BY country_code HAVING COUNT(*) > 1;", sep = ""))
```

Same countries are repeated more than once in all 4 surveys. Lets check there names.
```{r}
repeated_countries_string = paste("SELECT country_code FROM eddetails WHERE indicator_code = '", select_surveys_list[2], "' GROUP BY country_code HAVING COUNT(*) > 1", sep = "")

dbGetQuery(con, paste("SELECT DISTINCT country_name, country_code FROM eddetails WHERE country_code IN (", repeated_countries_string, ");"))
```
These countries or regions will be dropped later from common list.

Now merge these 4 dataframes of country codes into one with common names : inner join
```{r}
merged_country_codes = merge(country_list1, country_list2, by = 'country_code', all = FALSE)
merged_country_codes = merge(merged_country_codes, country_list3, by = 'country_code', all=FALSE)
merged_country_codes = merge(merged_country_codes, country_list4, by = 'country_code', all=FALSE)
```
```{r}
merged_country_codes
```

Now remove those 7 repeated country codes. Since they are regions, not countries, their all instances can be removed from the list.
```{r}

repeated_codes = dbGetQuery(con, paste("SELECT country_code FROM eddetails WHERE indicator_code = '", select_surveys_list[4], "' GROUP BY country_code HAVING COUNT(*) > 1;", sep = ""))[,1]

merged_country_codes = subset(merged_country_codes, !country_code %in% repeated_codes)

```

```{r}
merged_country_codes

```
Now we have a list of 189 countries that have exactly 1 occurence in all 4 surveys.

Create a dataframe for each survey.
```{r}
dbGetQuery(con, paste("SELECT * FROM eddetails WHERE indicator_code = '", select_surveys_list[4], "';", sep = ""))
```

First 32 entries are not countries but assembled regions for first 3 surveys. While for 4th survey, first 33 entries are not countries.

*Create and clean dataframe for female unemployment rate.*
```{r}

unemployment_fem_df = dbGetQuery(con, paste("SELECT * FROM eddetails WHERE indicator_code = '", select_surveys_list[1], "';", sep = ""))

#remove first 32 rows
unemployment_fem_df = unemployment_fem_df[33:nrow(unemployment_fem_df), ]

# removes countries' rows that are not in common list
unemployment_fem_df = subset(unemployment_fem_df, country_code %in% merged_country_codes[,1])

```

```{r}
head(unemployment_fem_df, 5)
```
```{r}
nrow(unemployment_fem_df)
```


*Create and clean dataframe for male unemployment rate.*
```{r}

unemployment_male_df = dbGetQuery(con, paste("SELECT * FROM eddetails WHERE indicator_code = '", select_surveys_list[2], "';", sep = ""))

#remove first 32 rows
unemployment_male_df = unemployment_male_df[33:nrow(unemployment_male_df), ]

# removes countries' rows that are not in common list
unemployment_male_df = subset(unemployment_male_df, country_code %in% merged_country_codes[,1])

```

```{r}
head(unemployment_male_df, 5)
```
```{r}
nrow(unemployment_male_df)
```


*Create and clean dataframe for female labor force in percentage.*
```{r}

labor_share_female_df = dbGetQuery(con, paste("SELECT * FROM eddetails WHERE indicator_code = '", select_surveys_list[3], "';", sep = ""))

#remove first 32 rows
labor_share_female_df = labor_share_female_df[33:nrow(labor_share_female_df), ]

# removes countries' rows that are not in common list
labor_share_female_df = subset(labor_share_female_df, country_code %in% merged_country_codes[,1])

```

```{r}
head(labor_share_female_df, 5)
```
```{r}
nrow(labor_share_female_df)
```


*Create and clean dataframe for countrymen studying abroad.*
```{r}

foreign_df = dbGetQuery(con, paste("SELECT * FROM eddetails WHERE indicator_code = '", select_surveys_list[4], "';", sep = ""))

#remove first 33 rows
foreign_df = foreign_df[34:nrow(foreign_df), ]

# removes countries' rows that are not in common list
foreign_df = subset(foreign_df, country_code %in% merged_country_codes[,1])

```

```{r}
head(foreign_df, 5)
```
```{r}
nrow(foreign_df)
```



**Dealing with missing values.**

*unemployment_fem_df*
```{r}
sapply(unemployment_fem_df, function(x) sum(is.na(x)))
```
```{r}
# dropping indicator_code and null value columns
unemployment_fem_df = subset(unemployment_fem_df, select = (c(country_name:country_code, x1991:x2014)))
# renaming rows
rownames(unemployment_fem_df) = 1:nrow(unemployment_fem_df)
```


*unemployment_male_df*
```{r}
sapply(unemployment_male_df, function(x) sum(is.na(x)))
```
```{r}
# dropping indicator_code and null value columns
unemployment_male_df = subset(unemployment_male_df, select = (c(country_name:country_code, x1991:x2014)))
# renaming rows
rownames(unemployment_male_df) = 1:nrow(unemployment_male_df)
```


*labor_share_female_df*
```{r}
sapply(labor_share_female_df, function(x) sum(is.na(x)))
```
Drop columns indicator_code, x1970 : x1989. Then impute remaining missing values by KNN.
```{r}
# dropping indicator_code and totally null value columns
labor_share_female_df = subset(labor_share_female_df, select = (c(country_name:country_code, x1990:x2014)))

# renaming rows
rownames(labor_share_female_df) = 1:nrow(labor_share_female_df)

```
KNN Imputation
```{r}

# Separate numeric columns and apply KNN imputation. Then merge along with others.
labor_share_female_df = merge( subset( labor_share_female_df, select = c(country_name:country_code) ), knnImputation( subset( labor_share_female_df, select = c(x1990:x2014) ) ), by=0, all = FALSE )

# Change data type of new column 'Row.names'. It formed automatically while merging on rownames.
labor_share_female_df$Row.names = as.numeric(as.character(labor_share_female_df$Row.names))
labor_share_female_df = labor_share_female_df[order(labor_share_female_df$Row.names),] # Set in original order
rownames(labor_share_female_df) = labor_share_female_df$Row.names # Reset Index
labor_share_female_df$Row.names = NULL
```

```{r}
# check if missing values are filled.
sapply(labor_share_female_df, function(x) sum(is.na(x)))
```


*foreign_df*
```{r}
sapply(foreign_df, function(x) sum(is.na(x)))
```
```{r}
# dropping indicator_code and totally null value columns
foreign_df = subset(foreign_df, select = (c(country_name:country_code, x1998:x2013)))

# renaming rows
rownames(foreign_df) = 1:nrow(foreign_df)
```



*Create folder to store csv files.*
```{r}
dir.create("plot_data")
```


*Store these dataframes into csv files.*
```{r}
write.csv(unemployment_fem_df, file = "plot_data/female_unemployment.csv", row.names = FALSE)
write.csv(unemployment_male_df, file = "plot_data/male_unemployment.csv", row.names = FALSE)
write.csv(labor_share_female_df, file = "plot_data/female_labor_share.csv", row.names = FALSE)
write.csv(foreign_df, file = "plot_data/foreign_education.csv", row.names = FALSE)
```

check by reading csv files.
```{r}
dff = read.csv(file = "plot_data/foreign_education.csv")
dff
```





```{r}
rm(dff)
```





```{r}
rm(list=ls())
```

```{r}
dbDisconnect(con)
```